Stateless Model Checking with Data-Race Preemption Points

### 2015-11-16 pldi-16/related.tex
add inspect to related work

{\bf Preempting at instruction granularity} is a prerequisite for using data-race PPs.
However, the resulting state space explosion demands that any such tool either
choose a small subset of instructions to consider as PPs
or be limited to very small test inputs.
%However, every such prior tool we know of has serious drawbacks.
SKI \cite{ski} approaches kernel code by choosing in advance a random set of instruction offsets from the start of the test,
which is more similar to stress testing or fuzzing than to exhaustive state space exploration.
SPIN \cite{spin} specializes in verifying synchronization primitive implementations such as RCU, which is very similar to our \mxtest~experiment.
However, SPIN is stateful rather than stateless, and explicitly storing visited program states rather than using DPOR limits the size of programs that can be practically tested.
SPIN also requires code to be written in the PROMELA DSL.
%so cannot check implementations directly.

>>>>

{\bf Preempting at instruction granularity} is a prerequisite for using data-race PPs.
However, the resulting state space explosion demands that any such tool either
choose a small subset of instructions to consider as PPs
or be limited to very small test inputs.
%However, every such prior tool we know of has serious drawbacks.
SKI \cite{ski} approaches kernel code by choosing in advance a random set of instruction offsets from the start of the test,
which is more similar to stress testing or fuzzing than to exhaustive state space exploration.
%
SPIN \cite{spin} specializes in verifying synchronization primitive implementations such as RCU, which is very similar to our \mxtest~experiment,
although it requires code to be written in the PROMELA DSL.
%However, SPIN is stateful rather than stateless, and explicitly storing visited program states rather than using DPOR limits the size of programs that can be practically tested.
%
Inspect \cite{inspect} instruments source code by inserting wrapper calls around all accesses to potentially-shared data.
It identifies such instructions in advance with an over-approximating alias analysis,
while \landslide~\cite{landslide} traces the memory locations of accesses at runtime.
Both SPIN and Inspect fix their set of PPs in advance, so could be combined with \quicksand~in future work.
%so cannot check implementations directly.
